### 2016-06-17 writeups/psycMethodsResponse2/response.tex

Results. Results for using different levels of compression for the random permutation model for the StackOverflow dataset are depicted in Figure 13. The plot is also broken out for different size datasets used to build the co-occurrence matrix.

Reducing compression to only 100 rows in the representation has a strong negative effect on accuracy, which shows that compression can influence model accuracy. However, 2048 rows is sufficient for these datasets, as increasing the number of rows to almost an order of magnitude higher (10,000) has little to no positive impact on accuracy, even for the highest corpus sizes.

Results are similar for Twitter. Figure 14 shows the same negative impact when reducing from 2048 to 100, and little to no impact when increasing from 2048 to 10,000. These results are consistent across all corpus sizes used to build the co-occurrence matrix.

Discussion. The fact that the random permutation model only needs around 2048 rows to represent all of the words in the Twitter and StackOverflow datasets is impressive. Twitter has around 2,383,000 unique words for the 3,000,000 tweets in each of the popular-users datasets. StackOverflow has 5,848,000 unique words for the 1,000,000 posts used to generate the co-occurrence matrix. This means that only 2048 rows are needed to represent most of the variance from all of the words in these co-occurrence matrices. This is likely because word use frequency for StackOverflow and Twitter approximately follows Zipf’s law. Stanley and Byrne (2013) showed that frequency of tag use for StackOverflow approximately follows a Zipf’s law distribution. This means that if the words are rank sorted by number of times they are used, the frequency of word use drops off sharply. Since these low-use words have little to no ability to influence predictions, it makes sense that accuracy does not substantially improve by providing additional dimensions for them.''
